---
title: "Assignment 5-Problem 3"
author: "Laura Ingulsrud"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3) Male and female salaries for starting postdoctoral and other employment positions (2015).
Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions: Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?


```{r} 
library(tidyverse)
library(knitr)
library(kableExtra)
library(plotly)
library(ggrepel)
library(extrafont)
library(pwr)
library(effsize)
library(vcdExtra)

#load packages needed

```

```{r}
med_sal_2015 <- read_csv("Med_Sal_2015.csv")
#read in data (data wrangled directly in excel)

med_sal_2015 
```

```{r}
med_sal_15_Employ <- med_sal_2015 %>% 
  select(Field, Male, Female, Status) %>% 
  filter(Status!= "Post_Doc")
med_sal_15_Employ

#made dataset for just Non_Post_Doc values

med_sal_15_PostDoc <- med_sal_2015 %>% 
  select(Field, Male, Female, Status) %>% 
  filter(Status!= "Non_Post_Doc")

#made dataset for just Post_Doc values

med_sal_15_PostDoc


```


```{r}
wsr_Employ_Gender <- wilcox.test(med_sal_15_Employ$Male, med_sal_15_Employ$Female, paired = TRUE)

#Run Wilcox Signed Rank for Non Post Doc dataset (significant value found)

wsr_Employ_Gender
```


```{r}
wsr_Post_Doc_Gender <- wilcox.test(med_sal_15_PostDoc$Male, med_sal_15_PostDoc$Female, paried = TRUE)

#Run Wilcox Signed Rank for Post Doc dataset (p-value is non-significant)

wsr_Post_Doc_Gender 
```

