---
title: "Assignment 5-Problem 3"
author: "Laura Ingulsrud"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3) Male and female salaries for starting postdoctoral and other employment positions (2015).
Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions: Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?


```{r} 
library(tidyverse)
library(knitr)
library(kableExtra)
library(plotly)
library(ggrepel)
library(extrafont)
library(pwr)
library(effsize)
library(vcdExtra)

#load packages needed

```

```{r}
med_sal_2015 <- read_csv("Med_Sal_2015.csv")
#read in data (data wrangled directly in excel)

med_sal_2015 
```

```{r}
med_sal_15_Employ <- med_sal_2015 %>% 
  select(Field, Male, Female, Status) %>% 
  filter(Status!= "Post_Doc")
med_sal_15_Employ

#made dataset for just Non_Post_Doc values

med_sal_15_PostDoc <- med_sal_2015 %>% 
  select(Field, Male, Female, Status) %>% 
  filter(Status!= "Non_Post_Doc")

#made dataset for just Post_Doc values

med_sal_15_PostDoc


```


```{r}
wsr_Employ_Gender <- wilcox.test(med_sal_15_Employ$Male, med_sal_15_Employ$Female, paired = TRUE)

#Run Wilcox Signed Rank for Non Post Doc dataset (significant value found)

wsr_Employ_Gender
```


```{r}
wsr_Post_Doc_Gender <- wilcox.test(med_sal_15_PostDoc$Male, med_sal_15_PostDoc$Female, paired = TRUE)

#Run Wilcox Signed Rank for Post Doc dataset (p-value is non-significant)

wsr_Post_Doc_Gender 
```



```{r}
med_sal_bar <- read_csv("Med_Sal_2015_bar chart.csv")

med_sal_bar_15_Employ <- med_sal_bar %>% 
  select(Field, Gender, Salary, Status) %>% 
  filter(Status!= "Post_Doc")

med_sal_bar_15_PostDoc <- med_sal_bar %>% 
  select(Field, Gender, Salary, Status) %>% 
  filter(Status!= "Non_Post_Doc")

Med_sal_barchart <- ggplot(med_sal_bar, aes(Field, Salary)) +
  geom_bar(aes(fill = Gender), width = 0.5, position = position_dodge(width = 0.6), stat = "identity") +
  theme(legend.position = "right", legend.title = element_blank(), axis.title.x = element_blank(), axis.title.y = element_blank()) +
  scale_x_discrete(breaks = c("Ag_sci_nat_resources", "Biological and biomedical sciences", "Health sciences", "Chemistry", "Geosciences, atmospheric, and ocean sciences", "Physics and astronomy", "Mathematics and computer sciences", "Psychology", "Economics", "Social sciences", "Engineering", "Education", "Humanities and arts", "Business management and administration", "Other non-S&E fields" )) +
  coord_flip() +
  facet_wrap(~Status)




Med_sal_barchart
```

