---
title: "Assignment 5-Problem 3"
author: "Laura Ingulsrud"
date: "11/28/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

3) Male and female salaries for starting postdoctoral and other employment positions (2015).
Compare median salaries for male and female doctorate recipients in 2015. Answer these two questions: Does median salary differ significantly between male and female starting postdoc positions? Does median salary differ significantly between male and female PhD recipients in non-postdoc employment positions?


```{r}
library(tidyverse)
library(knitr)
library(kableExtra)
library(plotly)
library(ggrepel)
library(extrafont)
library(pwr)
library(effsize)
library(vcdExtra)

```

```{r}
med_sal_2015 <- read_csv("Median salary for doctoral recipients.csv")
```

```{r}
med_sal_15_Employ <- med_sal_2015 %>% 
  select('Field of study', Employ_Male, Employ_Female)

med_sal_15_PostDoc <- med_sal_2015 %>% 
  select('Field of study', PostDoc_Male, PostDoc_Female)
```

